\Title

### 2016-03-10 manuscript/manuscript.tex
Fix citation to Silva 2001

Non-linear inversions for the relief of an interface (like the Moho)
are ill-posed and require additional constraints in the form of
regularization \citep{silva2001}.
A common approach is to use the first-order Tikhonov regularization to impose
smoothness on the solution.
The cost function for smoothness regularization is given by

>>>>

Non-linear inversions for the relief of an interface (like the Moho)
are ill-posed and require additional constraints in the form of
regularization \citep{silva2001b}.
A common approach is to use the first-order Tikhonov regularization to impose
smoothness on the solution.
The cost function for smoothness regularization is given by
